A Comparison of Synchronous-CFG \titlelinebreak{} Decoder Implementations

### 2013-07-16 mt-marathon.2013/PBML_article.tex
changes

\subsection{cdec and Joshua}
Moses implements a one-pass search strategy. All feature functions are evaluated when a hypothesis is created.

Joshua and cdec employs a multi-pass search strategy to translate each sentence. Each pass creates a hypergraph that is used as the input for the next pass. Both decoders evaluates stateless feature functions in the first pass, then stateful feature functions in the second.

cdec also supports an arbitrary number of passes, feature functions exactly to a particular pass.

\section{File Format}
\subsection{Old Framework}
Each feature function also required a separate section in the configuration (moses.ini) file to be created, along with the code to read the new section. For example, translation models are specified in the section
\begin{verbatim}
     [ttable-file]
\end{verbatim}
Language models in
\begin{verbatim}
     [lmodel-file]
\end{verbatim}
Furthermore, feature function also need a separate weight section, for example, for translation models:
\begin{verbatim}
     [weight-t]
\end{verbatim}
and language models:
\begin{verbatim}
     [weight-l]
\end{verbatim}
New feature functions need to create and manage their own specification and sections.

The features that can be tuned by MERT is also hardcoded in the tuning script. The MERT script has to be altered every time a new feature function is integrated into Moses.

\subsection{New Framework}
The configuration file format has been changed to minimize the amount of boilerplate code necessary when adding new feature functions. All feature functions are declared in the configuration file in the section
\begin{verbatim}
  [feature]
\end{verbatim}
In the fixed format
\begin{verbatim}
  Feature-Name [key=value]*
\end{verbatim}
For example,
\begin{verbatim}
  KENLM factor=0 path=lm.arpa order=5
\end{verbatim}
Similarly, all dense \emph{weights} are put into the section
\begin{verbatim}
  [weight]
\end{verbatim}
In the fixed format
\begin{verbatim}
  Feature-Instance= [value]*
\end{verbatim}
Weights for sparse features are in separate file referenced by the section
\begin{verbatim}
  [weight-file]
\end{verbatim}
in the format
\begin{verbatim}
  Feature-Instance feature value
\end{verbatim}

>>>>

\subsection{cdec and Joshua}
In contrast to Moses which uses a one-pass search strategy, cdec and Joshua uses a multi-pass search strategy. That is, for each input sentence, all feature functions are evaluated when a hypothesis is created in Moses.

In cdec and Joshua, each pass creates a hypergraph that is used as the input for the next pass. Both decoders evaluates stateless feature functions in the first pass, followed by stateful feature functions in the second.

cdec also supports an arbitrary number of passes, feature functions can be assigned to a particular pass.

cdec and Joshua do not partially evaluate stageful feature functions to estimate future cost, as done in Moses.

\section{File Format}
\subsection{Old Framework}
Each feature function also required a separate section in the configuration (moses.ini) file to be created, along with the code to read the new section. For example, translation models are specified in the section
\begin{verbatim}
     [ttable-file]
\end{verbatim}
Language models in
\begin{verbatim}
     [lmodel-file]
\end{verbatim}
Similarly, each feature function also need a separate weight section, for example, for translation models:
\begin{verbatim}
     [weight-t]
\end{verbatim}
and language models:
\begin{verbatim}
     [weight-l]
\end{verbatim}
New feature functions need to create and manage their own specification and weight sections.

The tuning script must also be informed of new weight sections by manually editing the MERT script.

\subsection{New Framework}
The configuration file format has been changed to minimize the amount of code changes necessary when adding new feature functions. All feature functions are declared in the configuration file in the section
\begin{verbatim}
  [feature]
\end{verbatim}
In the fixed format
\begin{verbatim}
  Feature-Name [key=value]*
\end{verbatim}
For example,
\begin{verbatim}
  KENLM factor=0 path=lm.arpa order=5
\end{verbatim}
Similarly, all dense \emph{weights} are put into the section
\begin{verbatim}
  [weight]
\end{verbatim}
In the fixed format
\begin{verbatim}
  Feature-Instance= [value]*
\end{verbatim}
Weights for sparse features are in separate file referenced by the section
\begin{verbatim}
  [weight-file]
\end{verbatim}
in the format
\begin{verbatim}
  Feature-Instance feature value
\end{verbatim}
